\vspace{-.5cm} Lights: a generalized joint model for high-dimensional multivariate longitudinal data and censored durations \vspace{.5cm}

### 2021-05-24 paper.tex
no more g_1 nor g_2 in R

Now, for the update of $\beta_k^{(w)}$ for $k=0, \ldots, K-1$, we similarly denote
\begin{equation*}
  R^{(w)}_{n,k}(\beta_k) = -n^{-1} \sum_{i=1}^n \hat \pi_{ik}^{\theta^{(w)}} \Big[ (y_i \odot \Phi_i^{(w)})^\top \hat \E_{\theta^{(w)}}[ M_{ik} | t_i, \delta_i, y_i] - \hat \E_{\theta^{(w)}}[ c_{\phi^{(w)}}(M_{ik}) | t_i, \delta_i, y_i] \Big]
\end{equation*}
based on the quantities involved in $\cQ_n(\theta, \theta^{(w)})$ depending on $\beta_k$, with $\tilde g_{i, t_j, {\gamma_k^0}^{(w)}, \gamma_k^{(w)}, \beta_k}^1$ and $\tilde g_{t_i, \gamma_k^{(w)}, \beta_k}^2$ defined in~\eqref{eq:g-tilde-1-2}. The integration over the survival process has been replaced with a finite sum over the process evaluated at the distinct event times $(t_1, \ldots, t_J)$ with $J \in~\N_+$, since $\lambda_0^{(w)}$ defined in~\eqref{eq:update_lambda_0} is always zero except at observed event times.
The update for $\beta_k^{(w)}$ therefore requires to solve the following convex minimization problem
\begin{equation}
  \label{eq:minimization-beta_k}
  \beta_k^{(w+1)} \in \argmin_{\beta_k \in \R^q} R^{(w)}_{n,k}(\beta_k) + \zeta_{2,k} \norm{\beta_k}_{\text{sg} l_1, \tilde{\eta}}.
\end{equation}
The previous trick we used to handle the non-differentiability of the $\ell_1$ part in the elastic net is no longer sufficient for~\eqref{eq:minimization-beta_k}, since the $\ell_2$ norm in the sparse group lasso is not squared, leading to a non-differentiability at 0 (which is precisely the criterion exploited by the penalty to set some groups of coefficients to exactly 0~\citep{simon2013sparse}). Then, we choose to solve problem~\eqref{eq:minimization-beta_k} using the proximal gradient descent~\citep{boyd2004convex} described in Algorithm~\ref{alg:ISTA}, where we first define
\[p_{\varrho}(y) = \argmin_u \Big\{\dfrac{1}{2\varrho} \left\lVert u - \big(y - \varrho  \nabla f(y) \big)\right\rVert_2^2 + \zeta \norm{u}_{\text{sg} l_1, \tilde{\eta}} \Big\}.\]

>>>>

Now, for the update of $\beta_k^{(w)}$ for $k=0, \ldots, K-1$, we similarly denote
\begin{equation*}
  R^{(w)}_{n,k}(\beta_k) = -n^{-1} \sum_{i=1}^n \hat \pi_{ik}^{\theta^{(w)}} \Big[ (y_i \odot \Phi_i^{(w)})^\top \hat \E_{\theta^{(w)}}[ M_{ik} | t_i, \delta_i, y_i] - \hat \E_{\theta^{(w)}}[ c_{\phi^{(w)}}(M_{ik}) | t_i, \delta_i, y_i] \Big]
\end{equation*}
based on the quantities involved in $\cQ_n(\theta, \theta^{(w)})$ depending on $\beta_k$. The integration over the survival process has been replaced with a finite sum over the process evaluated at the distinct event times $(t_1, \ldots, t_J)$ with $J \in~\N_+$, since $\lambda_0^{(w)}$ defined in~\eqref{eq:update_lambda_0} is always zero except at observed event times.
The update for $\beta_k^{(w)}$ therefore requires to solve the following convex minimization problem
\begin{equation}
  \label{eq:minimization-beta_k}
  \beta_k^{(w+1)} \in \argmin_{\beta_k \in \R^q} R^{(w)}_{n,k}(\beta_k) + \zeta_{2,k} \norm{\beta_k}_{\text{sg} l_1, \tilde{\eta}}.
\end{equation}
The previous trick we used to handle the non-differentiability of the $\ell_1$ part in the elastic net is no longer sufficient for~\eqref{eq:minimization-beta_k}, since the $\ell_2$ norm in the sparse group lasso is not squared, leading to a non-differentiability at 0 (which is precisely the criterion exploited by the penalty to set some groups of coefficients to exactly 0~\citep{simon2013sparse}). Then, we choose to solve problem~\eqref{eq:minimization-beta_k} using the proximal gradient descent~\citep{boyd2004convex} described in Algorithm~\ref{alg:ISTA}, where we first define
\[p_{\varrho}(y) = \argmin_u \Big\{\dfrac{1}{2\varrho} \left\lVert u - \big(y - \varrho  \nabla f(y) \big)\right\rVert_2^2 + \zeta \norm{u}_{\text{sg} l_1, \tilde{\eta}} \Big\}.\]
